Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-03 paper.qmd
Next steps for weather data

>>>>

# extract final view, draw with new axis display that
# only labels longer arrows, draw without red X

# cluster 4 only has two points, they are more in
# the center when optimizing for all outliers
# next step: check optimization for only cluster 4
# also cluster 3 might be of interest, it appears
# somewhat spread out in the final view, but it is
# also the largest cluster
